Digging Deeper Into the State of the Practice for Domain Specific Research Software

### 2022-02-18 StateOfPractice/Papers/ICCS-2022-SOP_MethodologyPlusExamples/DigDeep.tex
Revisions to Section 7: Threats To Validity

The measures in the measurement template~\cite{SmithEtAl2021} may not be broad
enough to accurately capture some qualities. For example, there are only two
measures of surface robustness. Similarly, reusability is assessed by the number
of code files and LOC per file, assuming that a large number of relatively small
files implies modularity. Furthermore, the measurement of understandability
relies on 10 random source code files. It is possible that the 10 files that
were chosen to represent a software package may not be a good representation.

Another risk to the validity of the proposed approach is missing or incorrect
data. Some software package data may not have been measured due to technology
issues like broken links. For the LBM example, this issue arose with the
measurement of Palabos, which had a broken link to its user manual. Some
pertinent data may not have been specified in public artifacts, or may be
obscure within an artifact or web-page. For the LBM example, the use of unit
testing and continuous integration was mentioned in the artifacts of only three
(ESPResSo, Ludwig, Musubi) packages. However, interviews suggested a more
frequent use of both unit testing and continuous integration in the development
processes.

>>>>

The measures in the measurement template~\cite{SmithEtAl2021} may not be broad
enough to accurately capture some qualities. For example, there are only two
measures of surface robustness. Similarly, reusability is assessed by the number
of code files and LOC per file, assuming that a large number of relatively small
files implies modularity. Furthermore, the measurement of understandability
relies on 10 random source code files. It is possible that the 10 files that
were chosen to represent a software package may not be representative.

Another risk to the validity of the proposed approach is missing or incorrect
data. Some software package data may have been missed due to technology
issues like broken links. For the LBM example, this issue arose with the
measurement of Palabos, which had a broken link to its user manual. Some
pertinent data may not have been specified in public artifacts, or may be
obscure within an artifact or web-page. For the LBM example, the use of unit
testing and continuous integration was mentioned in the artifacts of only three
(ESPResSo, Ludwig, Musubi) packages. However, interviews suggested a more
frequent use of both unit testing and continuous integration in the development
processes.
